\section{Anthony Onde Morada, MD}\label{anthony-onde-morada-md}

\subsection{Contact Information}\label{contact-information}

\textbf{Phone:} +1 (909) 239-3581\\
\textbf{Email:} anthony.omorada@gmail.com \textbar{}
amorada1@geisinger.edu\\
\textbf{Address:} 208 Main St.~Avoca, PA 18641\\
\textbf{ORCID:}
\href{https://orcid.org/0000-0002-0428-6558}{0000-0002-0428-6558}\\
\textbf{LinkedIn:}
\href{https://www.linkedin.com/in/anthonyomorada/}{anthonyomorada}\\
\textbf{GitHub:}
\href{https://github.com/anthonyomorada}{anthonyomorada}\\
\textbf{Twitter:}
\href{https://twitter.com/anthonyomorada}{@anthonyomorada}\\
\textbf{Instagram:}
\href{https://www.instagram.com/anthonyomorada/}{anthonyomorada}

\subsection{Professional Summary}\label{professional-summary}

General Surgery Resident (PGY-4) at Geisinger Northeast General Surgery
Program with over 10 years of translational and clinical research
experience. UCSB alum originally from Los Angeles, CA, currently based
in Scranton, PA. Proud Filipino-American physician (🇵🇭🇺🇸) with
demonstrated expertise in systematic reviews, clinical outcomes
research, and genomic medicine applications. Committed to advancing
surgical care through evidence-based practice and research innovation.

\subsection{Education}\label{education}

\textbf{Doctor of Medicine} \textbar{} 2022\\
Geisinger Commonwealth School of Medicine, Scranton, PA

\textbf{Bachelor of Science in Cell and Developmental Biology}
\textbar{} 2014\\
University of California -- Santa Barbara, Santa Barbara, CA\\
\emph{Graduated with Distinction in the Department of Molecular,
Cellular, and Developmental Biology}\\
\emph{Minor in English}

\textbf{Emergency Medical Technician Certification} \textbar{} 2011\\
UCLA Center for Prehospital Care, Los Angeles, CA\\
\emph{Accredited by West Los Angeles College}

\subsection{Current Position}\label{current-position}

\textbf{General Surgery Resident (PGY-4)} \textbar{} 2022 -- Present\\
Geisinger Northeast General Surgery Program, Scranton, PA

\subsection{Research Experience}\label{research-experience}

\textbf{Clinical Investigator and Analyst} \textbar{} 2020 -- 2022\\
Donald Guthrie Foundation, Guthrie Robert Packer Hospital, Sayre, PA -
Created prospective observational study to improve readmission rates in
patients with high-output ileostomy at risk for dehydration
(\href{https://clinicaltrials.gov/ct2/show/NCT04669964}{NCT04669964}) -
Developed protocol to improve general surgery resident surgical autonomy
through laparoscopic ventral hernia repair practice and
Self-Determination Theory

\textbf{Student Investigator} \textbar{} 2019 -- 2020\\
Quality Improvement Community Collaborative (QUICC) -- Transition Care
Management, Guthrie Robert Packer Hospital, Sayre, PA - Developed
prospective quality improvement project to increase transition care
management (TCM) order compliance in patients discharged from the
hospital - Created EPIC tool and educated staff to improve TCM order
appropriateness - Presented research entitled ``Optimizing Transition
Care Management Referrals to Primary Care Providers'' at Stanley Conklin
Research Day in April 2020

\textbf{Student Investigator} \textbar{} 2018 -- 2019\\
Longitudinal Community Health Improvement and Promotion (CHIP) --
Colorectal Cancer, Northeast Regional Cancer Institute, Scranton, PA -
Created prospective quality improvement project to improve colorectal
screening compliance at the Write Center Clinic in Clarks Summit, PA -
Developed protocol that allowed the Northeast Regional Cancer Institute
to call patients to remind and schedule patients for their colorectal
cancer screening - Presented protocol entitled ``Longitudinal Community
Health Research Project: Colorectal Cancer Screening'' at Geisinger
Commonwealth School of Medicine Research Day in March 2017

\textbf{Research Chair} \textbar{} 2018\\
General Surgery Interest Group (GSIG), Geisinger Commonwealth School of
Medicine, Scranton, PA - Organized meetings discussing innovative topics
in the field of general surgery - Generated research opportunities for
the club and its members - Presented four projects through collaborative
efforts at different local and national conferences

\textbf{Student Investigator} \textbar{} 2017 -- 2018\\
Weis Center for Research, Geisinger Medical Center, Danville, PA -
Evaluated genomic data of 92,297 patients enrolled in Geisinger's MyCode
and DiscovEHR program - Performed high volume statistical tests with R
programming analyzing patients' exome sequences - Awarded grant funding
from GCSOM's Summer Research Immersion Program

\textbf{Clinical Research Data Specialist} \textbar{} 2015 -- 2017\\
Departments of Liver Transplant \& Hepatobiliary and Pancreatic Surgery,
Cedars-Sinai Medical Center, Los Angeles, CA - Evaluated patient records
to assess the potential for inclusion in clinical research studies -
Coordinated biorepository including its database and collaborated with
co-investigators to provide specimens for translational research -
Performed independent literature searches, queried patient databases
with SQL, and performed statistical analyses using R programming for
publication purposes - Functioned as IRB contact for clinical trials and
IRB-approved datasets on pancreatic cancer, neuroendocrine tumors, and
liver tumors

\textbf{Clinical Research Volunteer} \textbar{} 2015\\
Department of Microbiology, St.~John's Regional Medical Center, Oxnard,
CA - Used R programming language to analyze blood culture data -
Measured the prevalence of blood culture contamination associated
organisms in laboratory results

\textbf{Undergraduate Research Assistant} \textbar{} 2013 -- 2015\\
Dr.~Kathy Foltz Laboratory, University of California -- Santa Barbara,
Santa Barbara, CA - Investigated egg activation mechanisms; reviewed
more than 8,000 unique phosphor-sequences from a high throughput
phosphoproteomic analysis of time course egg lysates of S. Purpuratus -
Awarded two Undergraduate Research and Creative Activities (URCA) Grants

\textbf{Laboratory Research Assistant} \textbar{} 2014\\
Dr.~Megan Valentine and Dr.~Stuart Feinstein Laboratories, University of
California -- Santa Barbara, Santa Barbara, CA - Laboratory assistant
for summer research project requiring synthesis of batches of
Alzheimer's associated protein, tau, and its isoforms - Tau Prep
protocol included: setting 6L of transformed bacterial culture while
inducing protein expression, preparing and executing SDS-PAGE, French
Press cell harvesting, Ion-Exchange Chromatography with
Phospho-Cellulose column, Hydrophobic Interaction Chromatography,
concentrating proteins with Amicon Ultra Concentrators, and determining
protein concentrations with LiCor

\textbf{Undergraduate Research Assistant} \textbar{} 2012\\
Dr.~Dzwokai Zach Ma Laboratory, University of California -- Santa
Barbara, Santa Barbara, CA - Researched histone covalent modifications
and their effects at the midbody during cytokinesis - Responsibilities
included: casting and running SDS-PAGE, E. coli transformation, total
immunostaining, western transfer, and cell lysis

\subsection{Clinical Experience}\label{clinical-experience}

\textbf{Lead Emergency Medical Technician} \textbar{} 2012 -- 2014\\
UCSB's Extra Help Program, Santa Barbara County Fire Department, Santa
Barbara, CA - Provided Basic Life Support care to the community of the
University of California -- Santa Barbara and associated districts;
responsible for more than 22,000 citizens - Acted as liaison between
student EMTs and Santa Barbara County Fire Department - Managed EMT
staff logistics and organized training sessions for continuing education
\#\# Publications

\subsubsection{Academic Manuscripts}\label{academic-manuscripts}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Bashiri A, \textbf{Morada A}, Sultany M, Senapathi S, Silverman S,
  Casós S, Behm R. Trends of Trauma Admissions in a Rural Trauma Center
  During Coronavirus Disease 2019 Pandemic. \emph{J Surg Res}. 2023
  Sep;289:202-210. doi: 10.1016/j.jss.2023.02.040. PMID: 37141703;
  PMCID: PMC10008796.
\item
  Keller HR, Senapathi SH, \textbf{Morada A}, Bertsch D, Cagir B.
  Survival in patients with neuroendocrine tumors of the colon, rectum
  and small intestine. \emph{Am J Surg}. 2023 Jan;225(1):58-65. doi:
  10.1016/j.amjsurg.2022.09.053. PMID: 36216612.
\item
  Sundaram N, \textbf{Morada A}, Bashiri A, Cagir B. CT images
  demonstrating the natural progression of locally advanced partially
  treated rectal cancer. \emph{BMJ Case Rep}. 2022 Mar 24;15(3):e247609.
  doi: 10.1136/bcr-2021-247609. PMID: 35332009; PMCID: PMC8948397.
\item
  \textbf{Morada AO}, Senapathi SH, Bashiri A, Chai S, Cagir B. A
  systematic review of primary ileostomy site malignancies. \emph{Surg
  Endosc}. 2022 Mar;36(3):1750-1760. doi: 10.1007/s00464-021-08847-7.
  PMID: 34997348. \href{../publications/2022-sr-ileostomy-malig.pdf}{📄
  PDF}
\item
  Senapathi H, \textbf{Morada A}, Perry M, Bertram C, Yeung E, Sultany
  M, Bertsch D, Cagir B. Prognostic Factors in Gastrointestinal
  Leiomyosarcomas: An Analysis Using the Surveillance, Epidemiology, and
  End Results (SEER) Database. \emph{Cureus}. 2021 Nov 10;13(11):e19447.
  doi: 10.7759/cureus. 19447. PMID: 34926025; PMCID: PMC8654067.
\item
  \textbf{Morada AO}, Scheidel C, Brown JL, Albright J, Kolade V, Cagir
  B. Predicting severe COVID-19 outcomes for triage and resource
  allocation. \emph{MedRxiv}. 2021.04.12.21255201.
  doi:10.1101/2021.04.12.21255201
\item
  Guo H, Garcia-Vedrenne AE, Isserlin R, Lugowski A, \textbf{Morada A},
  Sun A, Miao Y, Kuzmanov U, Wan C, Ma H, Foltz K, Emili A.
  Phosphoproteomic network analysis in the sea urchin Strongylocentrotus
  purpuratus reveals new candidates in egg activation.
  \emph{Proteomics}. 2015;15(23--24):4080--4095.
  doi:10.1002/pmic.201500159. PMID: 26572944.
\end{enumerate}

\subsubsection{Submitted or Prepared
Manuscripts}\label{submitted-or-prepared-manuscripts}

\begin{itemize}
\item
  Seungwoo C, Senapathi SH, \textbf{Morada AO}, Khaliq AA, Malviya B,
  Kolade V. Exploring the quality of internal medicine resident
  ambulatory patient care: a feasibility study of the patient-doctor
  relationship. \emph{Manuscript in preparation}
\item
  Dewar Z, \textbf{Morada AO}, Senapathi H, Rittenberger J. Ultrasound
  versus combined ultrasound and modified Seldinger technique in
  obtaining difficult peripheral intravenous access: A systematic review
  and meta-analysis of randomized clinical trials and cohort studies.
  \href{https://www.crd.york.ac.uk/PROSPERO/display_record.php?RecordID=210386}{PROSPERO
  CRD210386}. \emph{Manuscript in preparation}
\end{itemize}

\subsubsection{Peer Review Activities}\label{peer-review-activities}

\begin{itemize}
\tightlist
\item
  \textbf{Cancer Medicine} (2025) - Manuscript \#CAM4-2025-04-2129
\item
  \textbf{PLOS ONE} (2025) - Manuscript \#PONE-D-25-15492R (revision
  review)
\item
  \textbf{PLOS ONE} (2025) - Manuscript \#PONE-D-25-15492
\item
  \textbf{PLOS ONE} (2022) - Manuscript \#PONE-D-21-17071R1 (revision
  review)
\item
  \textbf{PLOS ONE} (2021) - Manuscript \#PONE-D-21-17071
\item
  \textbf{Frontiers in Pharmacology} (2022) - Manuscript \#1010820
\item
  \textbf{Annals of Internal Medicine} (2021) - Manuscript \#M21-2536
\end{itemize}

\subsubsection{Newspaper and Magazine
Articles}\label{newspaper-and-magazine-articles}

\begin{itemize}
\tightlist
\item
  \textbf{Morada AO}, Mackarey P. Finding your way clear of opioid
  problems. \emph{The Scranton Times-Tribune}. August 27, 2018, B7.
  \href{https://www.thetimes-tribune.com/news/finding-your-way-clear-of-opioid-problems-1.2378516}{Link}
\item
  \textbf{Morada A}. Ending Tuberculosis: A Global Commitment. \emph{The
  Traveler}. December 2017, Spring(1), 1.
\end{itemize}

\subsection{Presentations}\label{presentations}

\subsubsection{Oral Presentations}\label{oral-presentations}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Bashiri A, \textbf{Morada AO}, Silverman S, Behara M, Behm R. Trends
  of Trauma Admissions in a Rural Trauma Center During Coronavirus
  Disease 2019 Pandemic. \emph{Stanley Conklin Research Day}, Sayre, PA.
  April 2021.
\item
  Bertram C, Yeung E, Senapathi H, Perry M, \textbf{Morada A}, Bertsch
  D, Cagir B. Evaluation of the Survival outcomes of Intestinal
  Adenosquamous Carcinomas with SEER-18 registry: What do we know?
  \emph{Stanley Conklin Research Day}, Sayre, PA. April 2021.
\item
  Chai S, Kolade V, Senapathi SH, \textbf{Morada AO}, Khaliq AA, Malviya
  B. Exploring the quality of internal medicine resident ambulatory
  patient care: a feasibility study of the patient-doctor relationship.
  \emph{Stanley Conklin Research Day}, Sayre, PA. April 2021.
\item
  Senapathi SH, \textbf{Morada AO}, Morgan P, Cagir B. Comparing
  Epidemiology and Survival of Gastro-Intestinal Stromal Tumors and
  Leiomyosarcomas. \emph{Stanley Conklin Research Day}, Sayre, PA. April
  2021.
\item
  \textbf{Morada A}, Marinock J, Mirshahi U, Smelser DT, Carey DJ.
  Examining the Genetic Burden of Two Rare Autosomal Dominant Diseases.
  \emph{2018 Geisinger Commonwealth School of Medicine Summer Research
  Symposium}, Scranton, PA, August 2018.
\item
  \textbf{Morada A}, Mehta PA, Miller BN, Alagappan AA, Wachsman A,
  Gaddam S, Jamil L, Lo S, Nissen N. Management of Pancreatic Fistula or
  Leak after Pancreatectomy: Perspective from a 14-year Single Surgeon
  Experience. \emph{Southern California Chapter of the American College
  of Surgeons Annual Scientific Meeting}, Santa Barbara, CA, January
  2017.
\item
  Miller BN, \textbf{Morada A}, Gangi A, Annamalai AA, Wachsman A,
  Hendifar A, Tuli R, Nissen N. Challenging the Treatment Paradigm of
  Oligometastatic Pancreatic Adenocarcinoma with Selective Use of
  Locoregional Cytoreductive Therapies. \emph{Southern California
  Chapter of the American College of Surgeons Annual Scientific
  Meeting}, Santa Barbara, CA, January 2017.
\item
  Miller BN, Mehta PA, \textbf{Morada A}, Hendifar A, Annamalai AA,
  Wachsman A, Deepti D, Nissen N. Age-Related Differences in
  Presentation and Management of Pancreatic Neuroendocrine Tumors.
  \emph{Society of Surgical Oncology's 70th Annual Cancer Symposium},
  Seattle, WA, March 2017.
\end{enumerate}

\subsubsection{Poster Presentations}\label{poster-presentations}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Morada AO}, Senapathi SH, Bashiri A, Chai S, Cagir B. A
  Systematic Review of Primary Ileostomy Site Malignancies.
  \emph{Society of American Gastrointestinal and Endoscopic Surgeons
  2021 Meeting}, Las Vegas, NV, August 2021.
  \href{../presentations/2021-sages-poster.pdf}{🖼️ PDF}
\item
  Yeung E, Senapathi SH, \textbf{Morada AO}, Wung C, Miner J, Cagir B.
  High Output Ileostomy: A Retrospective Study on the Predictive
  Parameters of 30 Days Readmission from Dehydration. \emph{Society of
  American Gastrointestinal and Endoscopic Surgeons 2021 Meeting}, Las
  Vegas, NV, August 2021.
\item
  Chai S, Kolade V, Senapathi SH, \textbf{Morada AO}, Khaliq AA, Malviya
  B. Exploring the quality of internal medicine resident ambulatory
  patient care: a feasibility study of the patient-doctor relationship.
  \emph{Stanley Conklin Research Day}, Sayre, PA. April 2021.
\item
  Senapathi SH, \textbf{Morada AO}, Morgan P, Cagir B. Comparing
  Epidemiology and Survival of Gastro-Intestinal Stromal Tumors and
  Leiomyosarcomas. \emph{Stanley Conklin Research Day}, Sayre, PA. April
  2021.
\item
  Bertram C, Yeung E, Senapathi SH, Perry M, \textbf{Morada AO}, Bertsch
  D, Cagir B. Evaluation of the Survival outcomes of Intestinal
  Adenosquamous Carcinomas with SEER-18 registry: What do we know?
  \emph{Stanley Conklin Research Day}, Sayre, PA. April 2021.
\item
  Yeung E, Senapathi H, Perry M, Bertram C, \textbf{Morada AO}, Bertsch
  D, Cagir B. P90: Evaluation of the Survival Outcomes of Intestinal
  Adenosquamous Carcinomas with SEER-18 Registry: What Do We Know?
  \emph{Society of Surgical Oncology 2021: International Conference on
  Surgical Cancer Care}, Virtual Meeting. March 2021.
\item
  Senapathi SH, Perry M, \textbf{Morada AO}, Bertram C, Yeung E, Bertsch
  D, Cagir B. P85: Review of Intestinal Leiomyosarcomas: Epidemiology
  and Survival. \emph{Society of Surgical Oncology 2021: International
  Conference on Surgical Cancer Care}, Virtual Meeting. March 2021.
\item
  \textbf{Morada A}, Adnani A, Bombar B, Rodriguez A, Simpson K, Pamula
  J. Optimizing Transition Care Management Referrals to Primary Care
  Providers. \emph{Stanley Conklin Research Day}, Sayre, PA. April 2020.
\item
  Vaddadi S, Vyas N, Mathews K, \textbf{Morada A}, Hanrahan M,
  Santa-Lucia G, Davis G. An Artificial Intelligence Tool to Aid in the
  Management of Mechanical Ventilation: A Proof-of-Concept Study.
  \emph{Geisinger Commonwealth School of Medicine 2019 Spring Research
  Symposium}, Scranton, PA, March 2019.
\item
  Stewart J, Behrman J, Davis G, \textbf{Morada A}, Vyas N, Ali B,
  Watson S, Ca K, Sorour K. Retrospective evaluation of dependency on
  supplemental oxygen in patients undergoing therapeutic hypothermia.
  \emph{Geisinger Commonwealth School of Medicine 2019 Spring Research
  Symposium}, Scranton, PA, March 2019.
\item
  \textbf{Morada A}, Marinock J, Mirshahi U, Smelser DT, Carey DJ.
  Elucidating Rare Genetic Variants Associated with Autosomal Dominant
  Tubulointerstitial Kidney Disease. \emph{American College of Surgeons
  Clinical Congress 2019}, San Francisco, CA, October 2019.
\item
  \textbf{Morada A}, Teixeira A, Tripathi K, Reisch-Neyman Y, Davis G,
  Sorour O, Mccallion P, Sorour K. Intracolonic Administration of
  Vancomycin Via Cecal Tube in Intensive Care Unit Patients with
  Fulminant Clostridium Difficile Colitis. \emph{16th Annual American
  Medical Association Research Symposium}, National Harbor, MD, November
  2018.
\item
  \textbf{Morada A}, Marinock J, Mirshahi U, Smelser DT, Carey DJ.
  Elucidating Rare Genetic Variants Associated with Autosomal Dominant
  Tubulointerstitial Kidney Disease. \emph{2018 Geisinger Commonwealth
  School of Medicine Summer Research Symposium}, Scranton, PA, August
  2018.
\item
  Marinock J, \textbf{Morada A}, Mirshahi U, Smelser DT, Carey DJ. Rare
  Variants in APC Gene Increase Population Burden of Familial
  Adenomatous Polyposis. \emph{2018 Geisinger Commonwealth School of
  Medicine Summer Research Symposium}, Scranton, PA, August 2018.
\item
  Davis G, \textbf{Morada A}, Myers T, Sorour K. Effects of Body
  Temperature on Vasoactive-Inotropic Score. \emph{Annual National
  Student Research Forum}, Galveston, TX, May 2018.
\item
  Bolock A, Choudhary M, Fei X, Loser M, \textbf{Morada A}, Stefanelli
  M, Rwabukwisi F. Longitudinal Community Health Research Project:
  Colorectal Cancer Screening. \emph{Geisinger Commonwealth School of
  Medicine Research Day}, Scranton, PA, March 2017.
\item
  Miller BN, Garnett G, \textbf{Morada A}, Annamalai A, Hendifar A,
  Dhall D, Wachsman A, Yu R, Nissen N. Parenchymal-Preserving Resection
  for Pancreatic Neuroendocrine Tumors: are the Outcomes Justified?
  \emph{Society for Surgery of the Alimentary Tract 58th Annual Meeting
  at Digestive Disease Week 2017}, Chicago, IL, May 2017.
\item
  \textbf{Morada A}, Mehta PA, Miller BN, Annamalai A, Wachsman A,
  Gaddam S, Jamil L, Lo S, Nissen N. Pancreatic Fistula or Leak after
  Distal Pancreatectomy: Has anything changed? 13-year Single Surgeon
  Experience. \emph{Society for Surgery of the Alimentary Tract 58th
  Annual Meeting at Digestive Disease Week 2017}, Chicago, IL, May 2017.
\item
  Miao Y, \textbf{Morada A}, Sun A, Garcia-Vedrenne AE, Foltz KR. Egg
  Activation Signaling Networks Revealed Via High Throughput
  Phosphoproteomics. \emph{2015 Molecular, Cellular, and Developmental
  Biology Graduate Symposium}, Santa Barbara, CA, Feb 2015.
\item
  \textbf{Morada A}, Garcia-Vedrenne AE, Foltz KR. Investigating egg
  activation signaling circuits using high throughput phosphoproteomics.
  \emph{University of California -- Santa Barbara's Undergraduate
  Research Colloquium}, Santa Barbara, CA, May 2014.
\item
  \textbf{Morada A}, Garcia-Vedrenne AE, Foltz KR. Profiling and
  enrichment mapping of the sea urchin egg phosphoproteome in response
  to fertilization. \emph{University of California -- Santa Barbara's
  Undergraduate Research Colloquium}, Santa Barbara, CA, May 2013.
\end{enumerate}

\subsection{Honors and Awards}\label{honors-and-awards}

\begin{itemize}
\tightlist
\item
  \textbf{1st Place Oral Presentation}, Donald Guthrie Foundation
  Stanley Conklin Research Day (2021)
\item
  \textbf{1st Place Poster Presentation}, Donald Guthrie Foundation
  Stanley Conklin Research Day (2021)
\item
  \textbf{1st Place Hacking Health 2019 Winner}, Steel Institute for
  Health Innovation (\$5,000 award for ``ABBY'' - addressing provider
  burnout through EHR optimization)
\item
  \textbf{Certificate of Achievement for Pharmacology \& Toxicology}, UT
  Medical Branch National Student Research Forum (2018)
\item
  \textbf{Distinction and Certificate of Excellence}, GCSOM Summer
  Research Symposium (2018)
\item
  \textbf{1st Place Fundraising Team}, Pancreatic Cancer Action Network
  Purple Stride (2016, 2017) - Assistant Team Captain for Cedars-Sinai
  Whipplers
\item
  \textbf{Undergraduate Research and Creative Activities (URCA) Grants},
  UC Santa Barbara (2013, 2014)
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{Leadership and Extracurricular
Activities}\label{leadership-and-extracurricular-activities}

\textbf{Big Brother Mentor} \textbar{} 2017 -- Present\\
Big Brothers/Sisters -- Voluntary Action Center, Scranton, PA - Mentor a
matched ``little'' providing guidance and support

\textbf{Health Explorers Instructor} \textbar{} 2017 -- 2019\\
Regional Education Academy for Careers in Health Higher Education
Initiative (REACH-HEI), Geisinger Commonwealth School of Medicine,
Scranton, PA - Provide academic enrichment opportunities, including
mentoring, for low-income and first generation-to-college students in
northeastern and central Pennsylvania

\textbf{President and Community Service Chair} \textbar{} 2017 -- 2019\\
Asian Pacific American Medical Student Association (APAMSA), Geisinger
Commonwealth School of Medicine, Scranton, PA - Organized community
service events for APAMSA at GCSOM

\textbf{MD1 Class Representative and Research Chair} \textbar{} 2017 --
2019\\
General Surgery Interest Group (GSIG), Geisinger Commonwealth School of
Medicine, Scranton, PA - Liaison for first-year medical students to GSIG
leadership - Organized meetings discussing exciting topics in general
surgery - Generated research opportunities for club members

\textbf{Peer Mentor} \textbar{} 2018 -- 2019\\
MD Peer Mentorship Program, Geisinger Commonwealth School of Medicine,
Scranton, PA - Mentored and supported first- and second-year medical
students in their transition to the learning environment

\textbf{Team Abby Member} \textbar{} 2019\\
Hacking Health Competition, Geisinger Steel Institute for Health
Innovation, Danville, PA - First place \$5,000 winner for project
entitled ``Abby'' - Competed in multidisciplinary competition to create
solution for provider burnout and operational efficiencies

\textbf{Clinical Skills Chair} \textbar{} 2018 -- 2019\\
Plastic Surgery Interest Group, Geisinger Commonwealth School of
Medicine, Scranton, PA - Organized and led clinical skills workshops
such as suture clinics - Coordinated with gross anatomy lab and local
hospitals to create realistic simulation

\textbf{Co-President} \textbar{} 2018 -- 2019\\
Great Escapes Book Club, Geisinger Commonwealth School of Medicine,
Scranton, PA - Facilitated monthly book discussions that included
faculty, staff, and students

\textbf{Student Ambassador} \textbar{} 2017 -- 2018\\
Office of Admissions, Geisinger Commonwealth School of Medicine,
Scranton, PA - Volunteered on lunch panel events for prospective
students and interviewees - Provided tours of the college to
interviewees and hosted overnight accommodations

\textbf{Cedars-Sinai Whipplers Assistant Team Captain} \textbar{} 2016
-- 2017\\
Pancreatic Cancer Action Network (PanCAN), PurpleStride Los Angeles 5K
Walk/Run, Los Angeles, CA - Runner and fundraiser for Cedars-Sinai
Whipplers at PanCAN's PurpleStride fundraiser - Conducted outreach and
created advertising, leading to recruitment of more than 150 team
members and cumulative donation of \$200,000 over two years - Received
awards for being \#1 Fundraising Team for both 2016 and 2017 events

\textbf{Fight for Air Climber} \textbar{} 2016\\
American Lung Association, Fight for Air Climb at Aon Center, Los
Angeles, CA - Climber and fundraiser for the Cedars-Sinai We BeLUNG
Together Team at the American Lung Association's Fight for Air Climb
2016 at the Aon Center in Los Angeles - Assisted with raising more than
\$1500 for the Cedars-Sinai Team and climbed a 62-story building to
raise money in support of cardiopulmonary diseases

\textbf{Team KiPOW (Kid Power) Member} \textbar{} 2016\\
UC Irvine School of Medicine Pediatric Interest Group, Helen Estock
Elementary School in Tustin, CA - Taught 5th-grade students the benefits
of nutrition and exercise in support of Team KiPOW, which is a UCI/CHOC
advocacy program that empowers residents, medical students, and
undergraduates to serve as positive role models for the Orange County
pediatric population

\textbf{Physical Therapy Volunteer} \textbar{} 2014\\
Student Health, Physical Therapy, University of California -- Santa
Barbara, Santa Barbara, CA - Prepared patients for therapy using heat
and electrical stimulation and assist patients with physical therapy
exercises

\textbf{Clinical Care Extender Intern} \textbar{} 2013 -- 2014\\
COPE Health Solutions, St.~John's Regional Medical Center/Pleasant
Valley Medical Center, Oxnard, and Camarillo, CA - Volunteered on a
rotational basis through inpatient care, inpatient rehabilitation,
radiology, emergency medicine, and outpatient surgery

\subsection{Technical Skills and
Certifications}\label{technical-skills-and-certifications}

\textbf{Programming Languages:} R, Python, SQL\\
\textbf{Statistical Analysis:} High-volume genomic data analysis,
clinical research statistics\\
\textbf{Research Tools:} Literature search, database management,
biorepository coordination

\textbf{Certifications:} - AI for Medicine by DeepLearning.AI on
Coursera (2020) - Machine Learning by Stanford on Coursera (2017) -
Bleeding Control Basic -- American College of Surgeons, Committee on
Trauma (2017) - Data Science Specialization with R Programming by Johns
Hopkins University on Coursera (2016) - Emergency Medical Technician --
EMSA License E084811 (2011-2017)

\subsection{Cultural Competencies}\label{cultural-competencies}

\textbf{Transgender Conference} \textbar{} November 2017\\
Geisinger Commonwealth School of Medicine, Scranton, PA - Engaged in
training to learn and support unique health needs of transgender
individuals

\textbf{Safe Zone Trained} \textbar{} November 2017\\
Geisinger Commonwealth School of Medicine, Scranton, PA - Acquired
understanding of importance of language in creating affirming
environments for LGBTQ individuals

\textbf{Cross-Cultural Communication Trained} \textbar{} November 2017\\
Geisinger Commonwealth School of Medicine, Scranton, PA - Engaged in
interactive activity to experience how culture plays vital role in
navigating cultural spaces

\textbf{Microaggression Training} \textbar{} November 2017\\
Geisinger Commonwealth School of Medicine, Scranton, PA - Interactive
discussion regarding techniques to minimize microaggressions

\textbf{Community Action Poverty Simulation} \textbar{} November 2017\\
Geisinger Commonwealth School of Medicine, Scranton, PA - Interactive,
immersive experience to gain awareness of poverty and understand
experiences of those living in low-income environment

\textbf{Psychiatric Disability Empathy Training} \textbar{} November
2017\\
Geisinger Commonwealth School of Medicine, Scranton, PA - Three-hour
interactive training session on performing mental status exam in mock
psychiatric emergency room

\textbf{People with Disabilities as Teachers (PDAT) Training} \textbar{}
November 2017\\
Geisinger Commonwealth School of Medicine, Scranton, PA - Communication
with partners at Center for Independent Living to understand life and
interactions of those living with disabilities

\subsection{Personal Interests}\label{personal-interests}

\begin{itemize}
\tightlist
\item
  \textbf{Photography:} Nikon D60 with 50mm F/1.8G and 18-270mm
  F/3.5-6.3 lens
\item
  \textbf{Programming and Data Analytics:} Proficient with R and Python
  (GitHub profile: moradaao)
\item
  \textbf{Fantasy Sports:} 9-year basketball commissioner; basketball,
  football, and baseball champion
\item
  \textbf{Fitness:} Backpacking, bowling, cycling, hiking, lifting, and
  running
\end{itemize}
